%% cv.tex
%% Copyright 2017 Zeyi Fan
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2005/12/01 or later.
%
% This work has the LPPL maintenance status `maintained'.
%
% The Current Maintainer of this work is Zeyi Fan.
%
% This work consists of only the file cv.tex

\documentclass{article}
\usepackage[top=.4in, bottom=.0in, left=3in, right=0.4in,marginparwidth=2.5in]{geometry}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[absolute,overlay]{textpos}
\usepackage{fontspec}
\usepackage{titlesec}
\usepackage{pstricks}
\usepackage{amssymb}
\usepackage{paralist}

%\usepackage[pdfauthor={Zeyi Fan},
            %pdftitle={Zeyi Fan's Resume},
            %pdfkeywords={}]{hyperref}
\usepackage{hyperref}

\definecolor{mygray}{gray}{0.95}
\definecolor{lightdark}{gray}{0.55}
\definecolor{dark}{gray}{0.3}
\definecolor{skillbg}{gray}{0.7}

\newcommand{\amount}{5.7in}
\setcounter{section}{-1}

\linespread{1.2}
\pagenumbering{gobble}

\renewcommand{\labelitemi}{$\blacksquare$}
\renewenvironment{itemize}[1]{\begin{compactitem}#1}{\end{compactitem}}

% Helpers

\newcommand\twodigits[1]{%
   \ifnum#1<10 0#1\else #1\fi
}

%\newcommand\hl[1]{{\ralewaysb #1}}
\newcommand\hl[1]{#1}


% Fonts

\newfontfamily\raleway{Raleway}
\newfontfamily\ralewaym{Raleway Medium}
\newfontfamily\ralewaysb{Raleway SemiBold}
\newfontfamily\ralewayb{Raleway Bold}
\newfontfamily\ralewayeb{Raleway ExtraBold}
\newfontfamily\ralewaybb{Raleway Black}

\setmainfont{Raleway}


% Styles
\newcommand{\name}[2]{
    \begin{center}
        \Huge{
            \ralewayeb{#1 #2}
        }
    \end{center}
}

\newcommand{\tagline}[1]{
    \begin{center}
        \large{
            \color{dark}
            \ralewaysb{#1}
        }
        \vspace{.2em}
    \end{center}
}

\renewcommand{\thesection}{\twodigits{\arabic{section}}.}

\titleformat{\section}
[hang]
{\ralewaysb\large\color{dark}}
{}
{.0em}
{}
[{\titlerule[0.8pt]}]

\titlespacing*{\section}{0pt}{4pt}{10pt}

\setlength{\TPHorizModule}{1mm}
\setlength{\TPVertModule}{1mm}
\setlength{\parindent}{0mm}

\newcommand{\contactline}[2]{
    \ralewaysb{#1} & \raleway{#2}
}

\newcommand{\skill}[2]{
    \vspace{.2em}
    \ralewayb{#1}

    \psset{xunit=0.197\linewidth, yunit=5pt}
    \begin{pspicture}[showgrid=false](5,1)
        \psline[linecolor=skillbg](0,0.5)(5,0.5)
        \psline[linecolor=skillbg,arrows=|-|](1,0.5)(2,0.5)
        \psline[linecolor=skillbg,arrows=|-|](3,0.5)(4,0.5)
        \psline[linecolor=skillbg,arrows=-|](0,0.5)(5,0.5)

        \psline[linecolor=black,arrows=|-|](0,0.5)(#2,0.5)
    \end{pspicture}
}

\newcommand{\block}[3]{
    {\large\ralewayb #1}

    \ralewaym{\color{lightdark}#2}

    \raleway{#3}
}

\begin{document}

% background

\begin{tikzpicture}[remember picture,overlay]
  \fill[mygray] (current page.south west) rectangle ([xshift=-\amount]current page.north east);
\end{tikzpicture}

% Side Bar

\begin{textblock}{58.5}(6,7.7)
    \name{Zeyi}{Fan}

    %\tagline{Student \& Developer}

    \section{About me}

    \color{dark}

    Zeyi is a college student at San Jos\'{e} State University majoring in computer science. He is a passionate and self-taught programmer with experience in both front-end and back-end development. He is always thrilled to learn new technologies and use them into work.

    \section{Contacts}

    \renewcommand{\arraystretch}{1.1}

    \begin{tabular}{rl}
        \contactline{Phone}{(408) 618-9708} \\
        \contactline{Email}{i@zr.is} \\
        \contactline{Website}{\href{https://zr.is}{zr.is}} \\
        \contactline{GitHub}{\href{https://github.com/fanzeyi}{@fanzeyi}} \\
        \contactline{LinkedIn}{\href{https://linkedin.com/in/fanzeyi}{/in/fanzeyi}}
    \end{tabular}

    \section{Skills}

    \skill{Python}{4.5}

    \skill{JavaScript}{4}

    \skill{Java}{4}

    \skill{Go}{4}

    \skill{C/C++}{4}

    \skill{Git}{4}

    \skill{\TeX}{4}

    \skill{Scala}{4}

    \skill{Linux}{3}

    \skill{Nginx}{3}

    \skill{VimL}{3}

    \skill{PHP}{3}

    \skill{Ruby}{2.5}

    \skill{Haskell}{2}

\end{textblock}

% Main

\vspace{-25pt}  % Change this value to adjust the position of the right
\section{Education}

\block{San Jos\'{e} State University}
{B.S. Computer Science | GPA: 3.7 | Major GPA: 3.9 | Excepted May 2018}
{
    Relevant Coursework: Computer Architecture; Object-Oriented Design; Operating Systems; Programming Concepts and Paradigms.
}

\section{Work Experience}

\block{Front-end Engineer}
{Beary Innovation | Shenzhen, China (remote) | April 2014 - July 2014}
{
    \begin{itemize}[-]
        \item Joined Beary Innovation as their first employee.
        \item Responsible for the entire front-end development.
        \item Built their front-end skeleton with \hl{AngularJS and CoffeeScript}
    \end{itemize}
}

\vspace{.5em}

\block{Back-end Engineering Intern}
{Douban | Beijing, China | April 2013 - August 2013}
{

\begin{itemize}[-]
    \item Douban is an interest-based online community founded in 2003. It is the 10th largest website in China and it was invested by Sequoia Capital.
    \item Joined Douban as their youngest intern (during high school year).
    \item Responsible for developing an internal source code management system.
    \item Designed, and developed a REST service to \hl{encapsulate low-level git operations} with \hl{Python, Flask, and libgit2/pygit2.}
    \item Greatly sped up the performance of their source code managment system relying on git operations.
\end{itemize}
}

\section{Projects}

\block{Torchic}{}{
    \begin{itemize}[-]
        \item The project is built for Google's CodeU program.
        \item Designed and built a \hl{high-performance crawler in Go} with the ability to \hl{scale and disaster recovery}. It can crawl 400 pages per minute with single process.
        \item Used Redis as index database and MySQL as document database.
        \item \hl{Implemented BM25 as ranking algorithm.}
        \item Designed a responsive web page to serve search request for both mobile and desktop.
        \item The project is awarded Engineers' Choice judged by Googlers.
    \end{itemize}
}

\vspace{.5em}

\block{Kaname}{}{
    \begin{itemize}[-]
        \item Kaname is a desktop client for DoubanFM providing music streaming service.
        \item Built this project to explore Chrome's packaged appication API.
        \item Gained more than 10,000 users and an average 4.5 rating on Chrome Web Store.
        \item Built with \hl{CoffeeScript and UnderscoreJS.}
    \end{itemize}
}

\vspace{.5em}

\block{Vulpix}{}{
    \begin{itemize}[-]
        \item Vulpix is an online algorithm practicing system.
        \item Accpets C, C++ and Pascal program and the program will compile and run in a sandbox environment.
        \item Can effectively give feedbacks on time and memory performance of submitted program.
        \item Built with Python and Tornado as web framework.
    \end{itemize}
}

\section{Awards}

\ralewaysb Engineers' Choice \raleway at CodeU, Google\hfill Aug 2016

\ralewaysb 2nd Prize \raleway at Happy Day Hackathon, Douban\hfill July 2013

\ralewaysb The Most Popular and Creative Prize \raleway at Green Life Hackathon, Baidu\hfill July 2013

\ralewaysb National 2nd Prize \raleway at National Olympiad Informatics in Provinces, CCF\hfill Dec 2012

\end{document}
